%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning and Computer Vision Intern} % Job title
    {SHOPX} % Organization
    {Bangalore, India} % Location
    {May 2019 - July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Classified documents and generated bounding boxes for extracting relevant data like Aadhar, PAN and GSTIN number using Tensorflow.}
        \item {Generated synthetic data because of lack of sufficient data for training any neural-network model, used several pre-processing techniques to account for variations.}
        \item {Implemented various pre-processing techniques to enhance the network’s
        results and ended up choosing sauvola’s local thresholding with results varying with parameters.}
        \item {After carefully tuning the parameters and applying some document specific heuristics, were able to \textbf{outperform Google’s Cloud Vision} considerably on any randomly chosen test data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Under Prof. Sandeep Shukla sponsored by NUTANIX and UPSIDC} % Job title
    {IIT Kanpur Soc(Summer of code)} % Organization
    {IIT Kanpur, India} % Location
    {May 2018 - July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created web application Lexicon with motive to teach English and enhance vocabulary.}
        \item {Used php as server scripting language,and mysql for database-related queries.}
        \item {Had various features like up-voting a word and a trending section to promote the trending words.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
